\documentclass[sigplan,10pt]{acmart}

\settopmatter{printfolios=true,printccs=false,printacmref=false}

% minted 패키지 불러오기
\usepackage{caption}
\usepackage{minted}
\captionsetup{compatibility=false} % minted 캡션 옵션 충돌 방지
\usepackage[utf8]{inputenc}
\usepackage{tabularx}   % 표 열 너비 조절용
\usepackage{xcolor}  % 색상 지정용 (선택)
\usepackage[skip=5pt]{caption}  % skip 값으로 caption과 표 간의 간격 조정
\setlength{\belowcaptionskip}{0pt} % 표와 본문 간격 줄이기


\begin{document}

\title{Removing virtual stack in Emulation style LLVM-IR}

\author{Yujin An}
\affiliation{
  \institution{Chungnam National University}
  \country{Daejeon, South Korea}
}
\email{yujina@o.cnu.ac.kr}

\author{Sungho Lee}
\affiliation{
  \institution{Chungnam National University}
  \country{Daejeon, South Korea}
}
\email{eshaj@cnu.ac.kr}

\begin{abstract}
In recent years, static analysis of binary programs has attracted increasing
attention, especially in situations where the source code is unavailable.
Direct analysis of binaries, however, is challenging because much of the
original program information is lost during compilation. Binary lifters, which
translate binaries into an intermediate representation (IR), address this
limitation and have gained popularity. Recent work has shown that modern
lifters are capable of producing correct IR even for complex binaries.
Studies have also examined how the characteristics of lifter-generated LLVM IR
affect its applicability to different analysis tasks. Distinct styles of LLVM
IR have been identified, including Emulation-style IR (EIR) and High-level IR
(HIR). Experimental results show that HIR offers strong advantages for
analysis, while EIR provides higher functional accuracy. Conversely, HIR tends
to be weaker in preserving functionality, and EIR is less effective for certain
analyses.
This paper proposes a set of transformation rules to convert EIR into HIR, with
the goal of combining the functional accuracy of EIR with the analysis
advantages of HIR.
\end{abstract}

\maketitle

\input{sections/introduction}
\input{sections/approach_1}
\input{sections/approach_2}
\input{sections/conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{acmart}

\end{document}

